---
title: "Final analysis"
output:
    html_notebook:
        toc: yes
        toc_float: yes
---

# Data cleaning

## Load libraries

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(skimr)
library(knitr)
library(cowplot)
library(patchwork)
library(broom)
library(haven)
library(lubridate)
library(car)
library(parallel)
library(brms)
library(bayesplot)
library(tidybayes)
library(shinystan)
```

Set `cache = TRUE` as global option:

```{r}
knitr::opts_chunk$set(cache = TRUE)
```


## Import and clean data

Import the SPSS file. (It's better to import this versus a CSV file because the SPSS file has labels we can use to check that we're grabbing the right variables.)

```{r}
YA_spss <- read_sav("./data/NATSAP_YA_full.sav")
```


```{r}
names(YA_spss)
```

### Locate variables of interest

#### Demographic data

Gender:

```{r}
str(YA_spss$GENDER)
```

Date of birth is `YA_spss$ep01_dob`.

Date of admission is `YA_spss$ep01_doa`.

Date of discharge is `YA_spss$ep01_dod`.

#### Ethnicity

This appears in two places:

```{r}
str(YA_spss$ep01_ethnicity)
```

```{r}
str(YA_spss$ep01_client_NATSAP_ADULT_I_A0_Q17)
```

Do the two columns agree?

```{r}
check_ethnicity <- YA_spss %>%
    select(ethnicity1 = ep01_ethnicity,
           ethnicity2 = ep01_client_NATSAP_ADULT_I_A0_Q17) %>%
    transmute(ethnicity1 = as_factor(ethnicity1),
              ethnicity2 = as_factor(ethnicity2)) %>%
    group_by(ethnicity1, ethnicity2) %>%
    summarise(count = n(), .groups = "drop")
check_ethnicity
```

No, they don't match. We'll have to do some cleaning to merge these columns. We'll do this after we subset columns and remove data with missing values in key variables.

#### Intake questions

Affective motivation:

```{r}
str(YA_spss$ep01_client_NATSAP_ADULT_I_A0_Q10)
```

Cognitive motivation:

```{r}
str(YA_spss$ep01_client_NATSAP_ADULT_I_A0_Q13)
```

#### Discharge questions:

Satisfaction:

```{r}
str(YA_spss$ep01_client_NATSAP_ADULT_D_D0_Q5)
```

Effort:

```{r}
str(YA_spss$ep01_client_NATSAP_ADULT_D_D0_Q6)
```

#### OQ scores

Admit OQ:

```{r}
str(YA_spss$OQ_452_A_Total)
```

Discharge OQ:

```{r}
str(YA_spss$OQ_452_D_Total)
```

#### Program variables

Facility type:

```{r}
str(YA_spss$FacilityType)
```

### Select and format variables

```{r}
YA_clean_full <- YA_spss %>%
    dplyr::select(
        gender = GENDER,
        ethnicity1 = ep01_ethnicity,
        ethnicity2 = ep01_client_NATSAP_ADULT_I_A0_Q17,
        dob = ep01_dob,
        doa = ep01_doa,
        dod = ep01_dod,
        affective_motivation =
           ep01_client_NATSAP_ADULT_I_A0_Q10,
        cognitive_motivation =
           ep01_client_NATSAP_ADULT_I_A0_Q13,
        satisfaction = ep01_client_NATSAP_ADULT_D_D0_Q5,
        effort = ep01_client_NATSAP_ADULT_D_D0_Q6,
        OQ_admit = OQ_452_A_Total,
        OQ_discharge = OQ_452_D_Total,
        facility = ep01_facility_company,
        facility_type = FacilityType
           )
```

### Deal with date variables

Convert date variables to `datetime` format (for use with the `lubridate` package):

```{r}
YA_clean_full <- YA_clean_full %>%
    mutate(dob = as_datetime(dob),
           doa = as_datetime(doa),
           dod = as_datetime(dod))
```

Calculate age at admission:

```{r}
YA_clean_full <- YA_clean_full %>%
    mutate(age_at_admit = as.duration(interval(dob, doa)) %/%
               as.duration(years(1)))
```

### Remove values not from population of interest

```{r}
YA_clean_full <- YA_clean_full %>%
    filter(facility != "Morningside Recovery") %>%
    filter(age_at_admit < 30)
```

### Deal with factor variables:

```{r}
YA_clean_full$gender <- as_factor(YA_clean_full$gender)
YA_clean_full$ethnicity1 <- as_factor(YA_clean_full$ethnicity1)
YA_clean_full$ethnicity2 <- as_factor(YA_clean_full$ethnicity2)
YA_clean_full$affective_motivation <-
    as_factor(YA_clean_full$affective_motivation)
YA_clean_full$satisfaction <-
    as_factor(YA_clean_full$satisfaction)
YA_clean_full$effort <- as_factor(YA_clean_full$effort)
YA_clean_full$facility_type <- as_factor(YA_clean_full$facility_type)
```

Rename factors in `facility_type`. The current levels are:

```{r}
levels(YA_clean_full$facility_type)
```
We change "Residential Treatment Center" to "RTC" for convenience:

```{r}
levels(YA_clean_full$facility_type) <- c("RTC", "OBH")
levels(YA_clean_full$facility_type)
```

### Full data set (with missing values)

```{r}
skim(YA_clean_full) %>%
    knit_print()
```

### Write full data to file

```{r}
write_csv(YA_clean_full, "./data/YA_data_clean_full.csv")
```

### Remove missing data

`YA_clean_full` was the full data set. Now we remove missing data and call it `YA`.

```{r}
YA <- YA_clean_full %>%
    drop_na(gender, age_at_admit,
            affective_motivation, cognitive_motivation,
            satisfaction, effort,
            OQ_admit, OQ_discharge,
            facility, facility_type)
```

### Assign random IDs to facilities

Number of facilities:

```{r}
fac_list <- unique(YA$facility)
```

```{r}
n_fac <- length(fac_list)
n_fac
```

Generate random ID numbers:

```{r}
set.seed(1)
fac_ID <- sample(1:n_fac)
fac_ID
```

Create lookup table:

```{r}
names(fac_ID) <- fac_list
```

Assign new IDs for each facility:

```{r}
YA$fac_ID <- fac_ID[YA$facility]
```


### Ordered factors for Likert scales

Create ordered factors from Likert scales:

```{r}
table(YA$affective_motivation)
```

```{r}
YA$affective_motivation <- factor(YA$affective_motivation,
        levels = c("Very negative",
                   "Negative",
                   "Neutral",
                   "Somewhat positive",
                   "Very positive"),
        ordered = TRUE)
table(YA$affective_motivation)
```

```{r}
table(YA$satisfaction)
```

```{r}
YA$satisfaction <- factor(YA$satisfaction,
        levels = c("Very dissatisfied",
                   "Somewhat dissatisfied",
                   "Neutral",
                   "Somewhat satisfied",
                   "Very satisfied"),
        ordered = TRUE)
table(YA$satisfaction)
```

```{r}
table(YA$effort)
```

```{r}
YA$effort <- factor(YA$effort,
        levels = c("No effort",
                   "Little effort",
                   "Average effort",
                   "Above average effort",
                   "Maximum effort"),
        ordered = TRUE)
table(YA$effort)
```

### Center continuous variables

#### OQ admit:

```{r}
ggplot(YA, aes(x = OQ_admit)) +
    geom_histogram()
```

```{r}
mean(YA$OQ_admit)
```

#### Age at admit:

```{r}
ggplot(YA, aes(x = age_at_admit)) +
    geom_histogram(binwidth = 0.5, center = 0) +
    scale_x_continuous(breaks = seq(from = 18, to = 30))
```


```{r}
median(YA$age_at_admit)
```

#### Cognitive motivation:

```{r}
ggplot(YA, aes(x = cognitive_motivation)) +
    geom_histogram()
```

```{r}
median(YA$cognitive_motivation)
```

Center using either mean or median:

```{r}
YA$OQ_admit_meanc <- YA$OQ_admit - mean(YA$OQ_admit)
YA$age_at_admit_medc <-
    YA$age_at_admit - median(YA$age_at_admit)
YA$cognitive_motivation_medc <-
    YA$cognitive_motivation - median(YA$cognitive_motivation)
```

### Deal with ethnicity

```{r}
YA %>%
    unite("ethnicity", ethnicity1, ethnicity2, sep = "") %>%
    group_by(ethnicity) %>%
    summarize(count = n(), .groups = "drop") %>%
    as.data.frame() %>%
    print()
```
We just have to list these all out manually and classify them correctly.

```{r}
YA <- YA %>%
    unite("ethnicity", ethnicity1, ethnicity2, sep = "") %>%
    mutate(ethnicity_final =
        case_when(
            ethnicity == "0Hispanic" ~ "Hispanic/Latino",
            ethnicity == "0White" ~ "White",
            ethnicity == "African American" ~ "African American",
            ethnicity == "African AmericanAfrican American" ~ 
                "African American",
            ethnicity == "Asian American" ~ "Asian American",
            ethnicity == "AsianAsian American" ~ "Asian American",
            ethnicity == "CaucasianHispanic" ~ "Other",
            ethnicity == "CaucasianWhite" ~ "White",
            ethnicity == "Hispanic" ~ "Hispanic/Latino",
            ethnicity == "Hispanic or LatinoHispanic" ~
                "Hispanic/Latino",
            ethnicity == "Hispanic or LatinoOther" ~ "Other",
            ethnicity == "Hispanic/LatinoHispanic" ~ 
                "Hispanic/Latino",
            ethnicity == "Multi-EthnicOther" ~ "Other",
            ethnicity == "NA" ~ "Missing",
            ethnicity == "Native American" ~ "Native American",
            ethnicity == "Not Hispanic or LatinoAfrican American" ~ 
                "African American",
            ethnicity == "Not Hispanic or LatinoAsian American" ~ 
                "Asian American",
            ethnicity == "Not Hispanic or LatinoNative American" ~ 
                "Native American",
            ethnicity == "Not Hispanic or LatinoOther" ~ "Other",
            ethnicity == "Not Hispanic or LatinoWhite" ~ "White",
            ethnicity == "Other" ~ "Other",
            ethnicity == "White" ~ "White"))
```

```{r}
YA %>%
    group_by(ethnicity_final) %>%
    summarize(count = n(), .groups = "drop") %>%
    as.data.frame() %>%
    print()
```



## Final data set


```{r}
skim(YA) %>%
    knit_print()
```

### Write final data set to file

```{r}
write_csv(YA, "./data/YA_data_final.csv")
```



# Data summaries


## Summarize date variables

Date range:

```{r}
min(YA$doa)
max(YA$doa)
```
```{r}
min(YA$dod)
max(YA$dod)
```


## Summarize numerical variables

### OQ discharge

```{r}
summary(YA$OQ_discharge)
```

```{r}
ggplot(YA, aes(x = OQ_discharge)) +
    geom_histogram(binwidth = 10)
```

### OQ admit

```{r}
summary(YA$OQ_admit)
```

```{r}
ggplot(YA, aes(x = OQ_admit)) +
    geom_histogram(binwidth = 10)
```

```{r}
summary(YA$OQ_admit_meanc)
```

```{r}
ggplot(YA, aes(x = OQ_admit_meanc)) +
    geom_histogram(binwidth = 10)
```

### Cognitive motivation

```{r}
summary(YA$cognitive_motivation)
```

```{r}
ggplot(YA, aes(x = cognitive_motivation)) +
    geom_histogram()
```

```{r}
summary(YA$cognitive_motivation_medc)
```

```{r}
ggplot(YA, aes(x = cognitive_motivation_medc)) +
    geom_histogram()
```

### Age at admit

```{r}
summary(YA$age_at_admit)
```


```{r}
ggplot(YA, aes(x = age_at_admit)) +
    geom_histogram(binwidth = 1) + 
    scale_x_continuous(breaks = 18:29)
```

```{r}
summary(YA$age_at_admit_medc)
```

```{r}
ggplot(YA, aes(x = age_at_admit_medc)) +
    geom_histogram(binwidth = 1) + 
    scale_x_continuous(breaks = -2:9)
```


## Summarize categorical variables

### Gender

```{r}
YA %>%
    group_by(gender) %>%
    summarise(count = n(), .groups = "drop") %>%
    mutate(percent = prop.table(count) * 100)
```

### Ethnicity

```{r}
YA %>%
    group_by(ethnicity_final) %>%
    summarise(count = n(), .groups = "drop") %>%
    arrange(desc(count)) %>%
    mutate(percent = prop.table(count) * 100)
```

### Facility

```{r}
YA %>%
    select(facility, facility_type) %>%
    group_by(facility, facility_type) %>%
    summarise(count = n(), .groups = "drop") %>%
    group_by(facility_type) %>%
    summarise(count = n(), .groups = "drop")
```

```{r}
YA %>%
    group_by(facility_type) %>%
    summarise(sample_size = n(), .groups = "drop") %>%
    mutate(percent = prop.table(sample_size) * 100)
```



# Varying intercept model

## Model code

Default priors are good here:

```{r}
model_var_int <- brm(
    OQ_discharge ~ 1 +
        (1 | fac_ID) +
        gender +
        OQ_admit_meanc +
        age_at_admit_medc +
        facility_type +
        mo(affective_motivation) +
        cognitive_motivation_medc +
        mo(satisfaction) +
        mo(effort),
    data = YA,
    chains = 3,
    cores = parallel::detectCores() - 1,
    seed = 10,
    save_model = TRUE,
    file = "model_var_int"
    )
```

Check the data and model (especially to understand prior structure):

```{r}
data_var_int <- standata(model_var_int)
str(data_var_int)
```

```{r}
model_var_int$model
```

## Model summary

### Coefficients

```{r}
summary(model_var_int)
```

### Fixed effects

```{r}
fixef(model_var_int)
```

### Random effects

```{r}
ranef(model_var_int)
```

### Total effects (fixed effects plus random effects):

```{r}
coef(model_var_int)
```

### Conditional effects

```{r}
effects_var_int_affective_motivation_gender <-
    conditional_effects(model_var_int,
            effects = "affective_motivation:gender")
plot(effects_var_int_affective_motivation_gender,
     plot = FALSE)[[1]] +
     theme(axis.text.x =
               element_text(angle = 45, vjust = 1, hjust = 1)) 
```

```{r}
effects_var_int_affective_motivation_fac <-
    conditional_effects(model_var_int,
            effects = "affective_motivation:facility_type")
plot(effects_var_int_affective_motivation_fac,
     plot = FALSE)[[1]] +
     theme(axis.text.x =
               element_text(angle = 45, vjust = 1, hjust = 1)) 
```

```{r}
effects_var_int_cognitive_motivation_gender <-
    conditional_effects(model_var_int,
            effects = "cognitive_motivation_medc:gender")
plot(effects_var_int_cognitive_motivation_gender,
     plot = FALSE)[[1]]
```

```{r}
effects_var_int_cognitive_motivation_fac <-
    conditional_effects(model_var_int,
        effects = "cognitive_motivation_medc:facility_type")
plot(effects_var_int_cognitive_motivation_fac,
     plot = FALSE)[[1]]
```

```{r}
effects_var_int_satisfaction_gender <-
    conditional_effects(model_var_int,
                effects = "satisfaction:gender")
plot(effects_var_int_satisfaction_gender,
     plot = FALSE)[[1]] +    
     theme(axis.text.x =
               element_text(angle = 45, vjust = 1, hjust = 1)) 
```

```{r}
effects_var_int_satisfaction_fac <-
    conditional_effects(model_var_int,
                effects = "satisfaction:facility_type")
plot(effects_var_int_satisfaction_fac,
     plot = FALSE)[[1]] +    
     theme(axis.text.x =
               element_text(angle = 45, vjust = 1, hjust = 1)) 
```

```{r}
effects_var_int_effort_gender <-
    conditional_effects(model_var_int,
                effects = "effort:gender")
plot(effects_var_int_effort_gender, plot = FALSE)[[1]] +    
     theme(axis.text.x =
               element_text(angle = 45, vjust = 1, hjust = 1)) 
```

```{r}
effects_var_int_effort_fac <-
    conditional_effects(model_var_int,
                effects = "effort:facility_type")
plot(effects_var_int_effort_fac, plot = FALSE)[[1]] +    
     theme(axis.text.x =
               element_text(angle = 45, vjust = 1, hjust = 1)) 
```

```{r}
effects_var_int_OQ_admit_gender <-
    conditional_effects(model_var_int,
            effects = "OQ_admit_meanc:gender")
plot(effects_var_int_OQ_admit_gender,
     plot = FALSE)[[1]]
```

```{r}
effects_var_int_age_gender <-
    conditional_effects(model_var_int,
            effects = "age_at_admit_medc:gender")
plot(effects_var_int_age_gender,
     plot = FALSE)[[1]]
```


## Extract draws

```{r}
parnames(model_var_int)
```

```{r}
draws_p <- model_var_int %>%
    spread_draws(b_Intercept,
                 b_genderMALE,
                 b_OQ_admit_meanc,
                 b_age_at_admit_medc,
                 b_facility_typeRTC,
                 b_cognitive_motivation_medc,
                 bsp_moaffective_motivation,
                 bsp_mosatisfaction,
                 bsp_moeffort,
                 sd_fac_ID__Intercept,
                 sigma)
glimpse(draws_p)
```

```{r}
draws_p_gather <- model_var_int %>%
    gather_draws(b_Intercept,
                 b_genderMALE,
                 b_OQ_admit_meanc,
                 b_age_at_admit_medc,
                 b_facility_typeRTC,
                 b_cognitive_motivation_medc,
                 bsp_moaffective_motivation,
                 bsp_mosatisfaction,
                 bsp_moeffort,
                 sd_fac_ID__Intercept,
                 sigma)
glimpse(draws_p_gather)
```

```{r}
draws_mo <- model_var_int %>%
    spread_draws(simo_moaffective_motivation1[1:4],
                 simo_mosatisfaction1[1:4],
                 simo_moeffort1[1:4])
glimpse(draws_mo)
```

```{r}
draws_mo_gather <- model_var_int %>%
    gather_draws(simo_moaffective_motivation1[1:4],
                 simo_mosatisfaction1[1:4],
                 simo_moeffort1[1:4])
glimpse(draws_mo_gather)
```

```{r}
draws_r <- model_var_int %>%
    spread_draws(r_fac_ID[fac_ID, ])
glimpse(draws_r)
```

```{r}
draws_r_gather <- model_var_int %>%
    gather_draws(r_fac_ID[fac_ID, ])
glimpse(draws_r_gather)
```

## Posterior summaries

### Population

```{r}
draws_p %>%
    median_qi()
```

```{r}
draws_p_gather %>%
    median_qi()
```

### Monotonic ordinal

```{r}
draws_mo %>%
    median_qi()
```

```{r}
draws_mo_gather %>%
    median_qi()
```

BUT, medians will not add up to 100%. That's why we need means for the simo parameters:

```{r}
draws_mo %>%
    mean_qi()
```

```{r}
draws_mo_gather %>%
    mean_qi()
```

### Random effects

```{r}
draws_r %>%
    median_qi()
```

```{r}
draws_r_gather %>%
    median_qi()
```

## Posterior graphs

Simplify theme:

```{r}
theme_set(theme_tidybayes() + panel_border())
```

All credible intervals are 80% and 95%.

```{r}
draws_p_gather %>%
    filter(str_detect(.variable, "^b_")) %>%
    ggplot(aes(y = .variable, x = .value)) +
    stat_pointinterval()
```

```{r}
draws_p_gather %>%
    filter(.variable == "b_OQ_admit_meanc") %>%
    ggplot(aes(y = .variable, x = .value)) +
    stat_halfeye()
```

```{r}
draws_p_gather %>%
    filter(.variable == "b_Intercept") %>%
    ggplot(aes(y = .variable, x = .value)) +
    stat_halfeye()
```

```{r}
draws_p_gather %>%
    filter(.variable == "b_genderMALE") %>%
    ggplot(aes(y = .variable, x = .value)) +
    stat_halfeye()
```

```{r}
draws_p_gather %>%
    filter(.variable == "b_facility_typeRTC") %>%
    ggplot(aes(y = .variable, x = .value)) +
    stat_halfeye()
```

```{r}
draws_p_gather %>%
    filter(.variable == "b_cognitive_motivation_medc") %>%
    ggplot(aes(y = .variable, x = .value)) +
    stat_halfeye()
```

```{r}
draws_p_gather %>%
    filter(.variable == "b_age_at_admit_medc") %>%
    ggplot(aes(y = .variable, x = .value)) +
    stat_halfeye()
```

```{r}
draws_p_gather %>%
    filter(str_detect(.variable, "^bsp_")) %>%
    ggplot(aes(y = .variable, x = .value)) +
    stat_halfeye()
```

```{r}
draws_r %>%
    ggplot(aes(y = factor(fac_ID), x = r_fac_ID)) +
    stat_pointinterval()
```


## Posteriors for ordinal predictors

### Get all ordinal parts into one data frame

```{r}
draws_mo_unspread <- draws_mo %>%
    unspread_draws(simo_moaffective_motivation1[1:4],
                   simo_mosatisfaction1[1:4],
                   simo_moeffort1[1:4])
str(draws_mo_unspread)
```

```{r}
draws_bsp <- draws_p %>%
    select(starts_with("bsp_"), starts_with("."))
str(draws_bsp)
```

```{r}
draws_mo_all <- inner_join(draws_bsp, draws_mo_unspread,
                           by = ".draw") %>%
    select(-ends_with(".x")) %>%
    select(-ends_with(".y")) %>%
    mutate(affective_motivation_cum1 = 
               bsp_moaffective_motivation * 4 *
               `simo_moaffective_motivation1[1]`,
           affective_motivation_cum2 = 
               affective_motivation_cum1 +
               bsp_moaffective_motivation * 4 *
               `simo_moaffective_motivation1[2]`,
           affective_motivation_cum3 = 
               affective_motivation_cum2 +
               bsp_moaffective_motivation * 4 *
               `simo_moaffective_motivation1[3]`,
           affective_motivation_cum4 =
               affective_motivation_cum3 +
               bsp_moaffective_motivation * 4 *
               `simo_moaffective_motivation1[4]`,
           satisfaction_cum1 = 
               bsp_mosatisfaction * 4 *
               `simo_mosatisfaction1[1]`,
           satisfaction_cum2 = 
               satisfaction_cum1 +
               bsp_mosatisfaction * 4 *
               `simo_mosatisfaction1[2]`,
           satisfaction_cum3 = 
               satisfaction_cum2 +
               bsp_mosatisfaction * 4 *
               `simo_mosatisfaction1[3]`,
           satisfaction_cum4 = 
               satisfaction_cum3 +
               bsp_mosatisfaction * 4 *
               `simo_mosatisfaction1[4]`,
           effort_cum1 = 
               bsp_moeffort * 4 *
               `simo_moeffort1[1]`,
           effort_cum2 = 
               effort_cum1 +
               bsp_moeffort * 4 *
               `simo_moeffort1[2]`,
           effort_cum3 = 
               effort_cum2 +
               bsp_moeffort * 4 *
               `simo_moeffort1[3]`,
           effort_cum4 = 
               effort_cum3 +
               bsp_moeffort * 4 *
               `simo_moeffort1[4]`,)
glimpse(draws_mo_all)
```

### Summarize and plot

```{r}
draws_mo_all[1,]
```

```{r}
draws_mo_all %>%
    select(starts_with("aff")) %>%
    pivot_longer(starts_with("aff"),
                 names_to = "variable") %>%
    ggplot(aes(y = fct_rev(variable), x = value)) +
    stat_halfeye(point_interval = mean_qi)
```


```{r}
draws_mo_all %>%
    select(starts_with("sat")) %>%
    pivot_longer(starts_with("sat"),
                 names_to = "variable") %>%
    ggplot(aes(y = fct_rev(variable), x = value)) +
    stat_halfeye(point_interval = mean_qi)
```

```{r}
draws_mo_all %>%
    select(starts_with("eff")) %>%
    pivot_longer(starts_with("eff"),
                 names_to = "variable") %>%
    ggplot(aes(y = fct_rev(variable), x = value)) +
    stat_halfeye(point_interval = mean_qi)
```


# Final graphs for publication

```{r}
Q13_plot <- ggplot(YA, aes(x = cognitive_motivation)) +
    geom_histogram(binwidth = 3) +
    labs(title = "Histogram of responses to Q13 of 
NATSAP Adult Questionnaire-Initial:",
        subtitle = "\"It makes sense for me to be in a therapeutic program.\"",
        y = "Count",
        x = "Response")
Q13_plot
```

```{r}
Q10_plot <- ggplot(YA, aes(x = affective_motivation)) +
    geom_bar() +
    labs(title = "Bar chart of responses to Q10 of
NATSAP Adult Questionnaire-Initial:",
        subtitle = "\"How do you feel about being at this program?\"",
        y = "Count",
        x = "Response") +
     theme(axis.text.x =
               element_text(angle = 30, vjust = 1, hjust = 1))
Q10_plot
```
```{r}
Q5_plot <- ggplot(YA, aes(x = satisfaction)) +
    geom_bar() +
    labs(title = "Bar chart of responses to Q5 of
NATSAP Adult Questionnaire-Discharge:",
        subtitle = "\"Currently, how satisfied are you with the
quality of treatment you received at the program\"",
        y = "Count",
        x = "Response") +
     theme(axis.text.x =
               element_text(angle = 30, vjust = 1, hjust = 1))
Q5_plot
```
```{r}
Q6_plot <- ggplot(YA, aes(x = effort)) +
    geom_bar() +
    labs(title = "Bar chart of responses to Q6 of
NATSAP Adult Questionnaire-Discharge:",
        subtitle = "\"How much effort did you put into your treatment at the program?\"",
        y = "Count",
        x = "Response") +
     theme(axis.text.x =
               element_text(angle = 30, vjust = 1, hjust = 1))
Q6_plot
```
```{r, fig.height = 10, fig.width = 10}
wrap_plots(Q13_plot, Q10_plot, Q5_plot, Q6_plot)
```

```{r, fig.width = 8}
draws_p_gather %>%
    filter(str_detect(.variable, "^bsp_")) %>%
    mutate(.variable = factor(.variable, levels = c("bsp_moeffort",
                                                    "bsp_mosatisfaction",
                                                    "bsp_moaffective_motivation"))) %>%
    ggplot(aes(y = .variable, x = .value)) +
    stat_halfeye(point_interval = mean_qi) +
    labs(title = "Posterior distributions for the coefficients of monotonic ordinal
regressors, with means and 80%/95% credible intervals.",
         subtitle = "Coefficient values represent the average change in OQ discharge score
predicted by the model between one level of the ordinal predictor and the next.",
         y = "Coefficient",
         x = "Coefficient value") +
    scale_y_discrete(labels = c("effort",
                                "satisfaction",
                                "affectivemotivation")) +
    geom_vline(xintercept = 0)
```

```{r, fig.width = 8}
draws_mo_all %>%
    select(starts_with("aff")) %>%
    pivot_longer(starts_with("aff"),
                 names_to = "variable") %>%
    ggplot(aes(y = fct_rev(variable), x = value)) +
    stat_halfeye(point_interval = mean_qi) +
    labs(title = "Posterior distributions for the predicted changes in OQ
discharge score at each level of affective motivation,
with means and 80%/95% credible intervals",
        subtitle = "Each level is relative to the baseline value of \"Very negative.\"",
         y = "Levels of affective motivation",
         x = "Predicted OQ discharge score change") +
    scale_y_discrete(labels = c("Very positive",
                                "Somewhat positive",
                                "Neutral",
                                "Negative")) +
    lims(x = c(-42, 4)) +
    geom_vline(xintercept = 0)
```

```{r, fig.width = 8}
draws_mo_all %>%
    select(starts_with("sat")) %>%
    pivot_longer(starts_with("sat"),
                 names_to = "variable") %>%
    ggplot(aes(y = fct_rev(variable), x = value)) +
    stat_halfeye(point_interval = mean_qi) +
    labs(title = "Posterior distributions for the predicted changes in OQ
discharge score at each level of satisfaction,
with means and 80%/95% credible intervals",
        subtitle = "Each level is relative to the baseline value of \"Very dissatisfied.\"",
         y = "Levels of satisfaction",
         x = "Predicted OQ discharge score change") +
    scale_y_discrete(labels = c("Very satisfied",
                                "Somewhat satisfied",
                                "Neutral",
                                "Somewhat dissatisfied")) +
    lims(x = c(-42, 4)) +
    geom_vline(xintercept = 0)
```

```{r, fig.width = 8}
draws_mo_all %>%
    select(starts_with("eff")) %>%
    pivot_longer(starts_with("eff"),
                 names_to = "variable") %>%
    ggplot(aes(y = fct_rev(variable), x = value)) +
    stat_halfeye(point_interval = mean_qi) +
    labs(title = "Posterior distributions for the predicted changes in OQ
discharge score at each level of effort,
with means and 80%/95% credible intervals",
        subtitle = "Each level is relative to the baseline value of \"No effort.\"",
         y = "Levels of effort",
         x = "Predicted OQ discharge score change") +
    scale_y_discrete(labels = c("Maximum effort",
                                "Above average effort",
                                "Average effort",
                                "Little effort")) +
    lims(x = c(-42, 4)) +
    geom_vline(xintercept = 0)
```


# Tables (not formatted yet)

All model coefficients:

```{r}
summary(model_var_int, priors = TRUE)
```

Random effects (deviations from overall intercept for each of the 21 programs):

```{r}
ranef(model_var_int)
```
